>

### 2022-02-07 notebook/_posts/2020-11-12-leopold2020host-bias-sensitivity/index.Rmd
Update post metadata
Fixed date in YAML to match folder date; removed superfluous 'R' tag

---
title: >
  Exploring the effect of bias in Leopold and Busby (2020)
author: Michael McLaren
date: '2019-10-21'
categories:
  - bias sensitivity
  - R
  - ref:leopold2020host
description:
bibliography: _references.bib
draft: false
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_float: true
    dev: svg
---

@@

```{r load-data, include = FALSE}
## From the metacal 2.0 tutorial
# Download data from https://zenodo.org/record/3872145
data_path <- here::here("_data", "leopold2020host")
# To use a temporary directory:
# data_path <- file.path(tempdir(), "leopold2020")
if (!dir.exists(data_path)) {
  dir.create(data_path, recursive = TRUE)
  download.file(
    "https://zenodo.org/record/3872145/files/dleopold/Populus_priorityEffects-v1.2.zip",
    file.path(data_path, "Populus_priorityEffects-v1.2.zip")
  )
  unzip(
    file.path(data_path, "Populus_priorityEffects-v1.2.zip"), 
    exdir = data_path
  )
}
#> The microbiome data is stored in a phyloseq object,
ps <- file.path(data_path, 
  "dleopold-Populus_priorityEffects-8594f7c/output/compiled/phy.rds") %>%
  readRDS

>>>>

---
title: >
  Exploring the effect of bias in Leopold and Busby (2020)
author: Michael McLaren
date: '2020-11-10'
categories:
  - bias sensitivity
  - ref:leopold2020host
description:
bibliography: _references.bib
draft: false
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_float: true
    dev: svg
---

@@

```{r load-data, include = FALSE}
## From the metacal 2.0 tutorial
# Download data from https://zenodo.org/record/3872145
data_path <- here::here("notebook/_data", "leopold2020host")
# To use a temporary directory:
# data_path <- file.path(tempdir(), "leopold2020")
if (!dir.exists(data_path)) {
  dir.create(data_path, recursive = TRUE)
  download.file(
    "https://zenodo.org/record/3872145/files/dleopold/Populus_priorityEffects-v1.2.zip",
    file.path(data_path, "Populus_priorityEffects-v1.2.zip")
  )
  unzip(
    file.path(data_path, "Populus_priorityEffects-v1.2.zip"), 
    exdir = data_path
  )
}
#> The microbiome data is stored in a phyloseq object,
ps <- file.path(data_path, 
  "dleopold-Populus_priorityEffects-8594f7c/output/compiled/phy.rds") %>%
  readRDS
